%!TEX root = ../main.tex
\chapter{Iterim review}
\textbf{Student: Andrei Butnaru} \textbf{Supervisor: Alexios Mylonas}


\tocless\section{Define the problem}

\begin{mdframed}
    Has the problem been defined, has the artefact been identified and have objectives been set?
    \textbf{Yes}
\end{mdframed}

\tocless\section{Review of Other Work}
\begin{mdframed}
    Is there evidence of appropriate research?
    \textbf{Yes}
\end{mdframed}

\tocless\section{Analysis, Design \& Implementation of Artefact}
\begin{mdframed}
    Is there evidence of appropriate analysis of the problem and development of a solution?
    \textbf{Yes}
\end{mdframed}

\tocless\section{Dissertation}
\begin{mdframed}
    Have sections of the dissertation been written and has the Supervisor seen these?
    \textbf{Yes}
\end{mdframed}

\tocless\section{Planning \& Progress}
\begin{mdframed}
    Is there an acceptable plan for this project and is it being followed?
    \textbf{To some extent}
\end{mdframed}

\textbf{Comments:} The plan has been adjusted, some delays due to the lockout.

    \textbf{Overall Assessment} Satisfactory

\clearpage
\begin{mdframed}

    \textbf{Date:} March 27

    {\parindent0pt \textbf{Signed:} }

    Supervisor: ....Alexios....

    Student: ....Andrei....

\end{mdframed}


• Supervisor to retain the signed form and supply the student with a copy if required.

• Supervisor to upload the form on Brightspace and grade the student as Satisfactory, Requires Major Improvement, Requires Minor Improvement or Unsatisfactory.

• Supervisor to notify the Project Coordinator if the student is at risk of failing the project or not engaging.